Spreading of a Facebook Application

### 2011-04-15 paper.tex
abstract updated

\cortext[cor1]{Corresponding author}
\cortext[cor2]{Principal corresponding author}
\fntext[fn1]{This document is a collaborative effort.}
%\fntext[fn2]{Another author footnote, but a little more longer.}
%\fntext[fn3]{Yet another author footnote. Indeed, you can have
%xany number of author footnotes.}
\tnotetext[tn1]{This is a specimen title.}

\begin{abstract}
%% Text of abstract, 150 - 350 words
% The outcome was students' perceptions of preparedness.
Applications on Facebook are popular and attract many
people. Nevertheless, before installation people must acknowledge that an application
exists, and they must demand the application, too.
There may exist several reasons for people to install
applications, such as intensive usage within their social network, or
personal interest in a special topic. Persuasion can
happen virally through Facebook's news stream, by marketing through
friends, or by directed search on 
Facebook. Differences in the spreading process are supposed to exist
for the different kinds of applications.

This paper investigates, how a quiz asking people five randomly
selected questions about dentistry health facts spreads on
Facebook. The quiz is made social by providing participants with
information such as if they were better than their
friends and other users, and which of their friends could answer the given questions.

@@

Results show that participants, who connect the network of existing
users to a new one, often achieved a relatively high score in the quiz. New
participants often had strong connections to the network of people who
already participated. Indeed, the number of friends did not seem to make
users more or less likely to gather new participants for the quiz.
\end{abstract}

@@

\begin{table}
\label{tab:scorespread}
\begin{tabular}{c c}
Spread to & Concerned People & Average score \\ 
1&	4 & 2.75 \\
2&	3&3.96 \\
3&	1&3 \\
\end{tabular}
\caption{Table details the average score of people who spread the
  application to one, two, or three users, as well as the number of
  concerned people.}
\end{table}

>>>>

%\cortext[cor1]{Corresponding author}
%\cortext[cor2]{Principal corresponding author}
%\fntext[fn1]{This document is a collaborative effort.}
%\fntext[fn2]{Another author footnote, but a little more longer.}
%\fntext[fn3]{Yet another author footnote. Indeed, you can have
%xany number of author footnotes.}
%\tnotetext[tn1]{This is a specimen title.}

\begin{abstract}
%% Text of abstract, 150 - 350 words
% The outcome was students' perceptions of preparedness.
Applications on Facebook are popular and attract many
people. Nevertheless, before installation people must acknowledge that an application
exists, and they must demand the application, too.
There may exist several reasons for people to install
applications, such as intensive usage within their social network or
personal interest in a special topic. Persuasion can
happen virally by Facebook's news stream, by marketing through
friends, or by directed search on 
Facebook. Differences in the spreading process are supposed to exist
for the different kinds of applications.

This paper investigates how a quiz, asking people five randomly
selected questions about dentistry health facts, spreads on
Facebook. The quiz is endowed with a social component: After
completion participants get more than the solution solely. Instead,
users can see images of friends who could answer the questions they got correctly
underneath the solution. In addition, they are told how good their
score was in comparison to their friends.

@@

Results show that participants who connect the network of existing
users to a new one often achieved a relatively high score in the quiz. New
participants often had strong connections to the network of people who
already participated. Indeed, the number of friends did not seem to make
users more or less likely to gather new participants for the quiz.
\end{abstract}

@@

\begin{table}
\label{tab:scorespread}
\begin{tabular}{c c c}
Spread to & Concerned People & Average score \\ 
1&	4 & 2.75 \\
2&	3&3.96 \\
3&	1&3 \\
\end{tabular}
\caption{Table details the average score of people who spread the
  application to one, two, or three users, as well as the number of
  concerned people.}
\end{table}
